The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update (ish) nobs discussion

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage <!-- TODO: check this fig
A/C similar lines--> Individuals in summer layers had consistent weak
connections. Layer relevance was stable in winter for open and forest habitats
but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance
was stable for all habitat classes in summer layers. Layer similarity was stable
for forest and open, except for a sharp decrease in layer similarity in open at
100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species. <!-- TODO:
how? This isn't clear enough for me to follow yet -->

<!-- TODO: update this..... -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts.

>>>>

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage <!-- TODO: check this fig
A/C similar lines--> Individuals in summer layers had consistent weak
connections. Layer relevance was stable in winter for open and forest habitats
but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance
was stable for all habitat classes in summer layers. Layer similarity was stable
for forest and open, except for a sharp decrease in layer similarity in open at
100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize.
Mean graph strength varied in winter layers becoming stable at ~200 m and remained consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in winter layers increased between ~10 - ~50 observations, remaining stable with additional observations (Figure \@ref(fig:nobs)b). 
<!-- TODO: update with fix for open/rerun -->
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and therefore layer similarity could
not be calculated below approximately <!--TODO: update these -->75 observations for forest, approximately 
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased dramatically between ~10 - ~50 observations before stabilizing with all new observations included (Figure \@ref(fig:nobs)d). 
Given the observed trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.
